05_DESeq_manipulation

### 2019-05-19 analysis/05_DESeq2_manipulate.Rmd
run all

allcontrasts <- totalDEGS %>%
  ggplot( aes(V1, V2)) +
    geom_tile(aes(fill = V3)) +
    scale_fill_viridis(na.value="#FFFFFF00", 
                     limits = c(0, 3000),
                     breaks = c(0, 1000, 2000, 3000)) + 
    xlab(" ") + ylab("Timepoint") +
    labs(fill = "# of DEGs",
         subtitle = "eachgroup")
plot(allcontrasts)

@@

pca1 <- ggplot(pcadata, aes(treatment, PC1,color = treatment)) + 
  geom_boxplot() +
  ylab(paste0("PC1: ", percentVar[1],"% variance")) +
  xlab(NULL) +
  theme_cowplot(font_size = 8, line_size = 0.25) +
  labs(subtitle = "eachgroup") +
  theme(legend.position = "none")

pca2 <- ggplot(pcadata, aes(treatment, PC2,color = treatment)) + 
  geom_boxplot() +
  ylab(paste0("PC2: ", percentVar[2],"% variance")) +
  xlab(NULL) +
  theme_cowplot(font_size = 8, line_size = 0.25) +
  labs(subtitle = "eachgroup") +
  theme(legend.position = "none")

@@

sigDEGs <- as.matrix(sigDEGs) 
pheatmap(sigDEGs, show_rownames = F, show_colnames = F,
         color = viridis(30),
         breaks=myBreaks,
         annotation_col=anndf,
         main = "eachgroup")

pheatmap(sigDEGs, kmeans_k = 5,
         show_rownames = F, show_colnames = F,
         color = viridis(30),
         breaks=myBreaks,
         annotation_col=anndf,
         main = "eachgroup")

@@

# make dataframe with geneids and names and counts

candidates <- full_join(geneinfo, DEGs)
drop.cols <-colnames(candidates[,grep("padj|pval|pmin", colnames(candidates))])
candidates <- candidates %>% dplyr::select(-one_of(drop.cols))
candidates <- candidates %>%
  filter(Name %in% c( #"JUN", "JUND", "EGR",  "AVP", "AVPR1A", "AVPR1B", "AVPR2", "OXT",  
                     "AR", "CYP19A1", "ESR1", "ESR2", "FSHR",
                     "GHRL", "GAL", "NPVF", "GNRH1", "LHCGR",
                     "PGR", "PRL", "PRLR", "VIP", "VIPR1")) 
row.names(candidates) <- candidates$Name
candidates <- candidates %>% select(-row.names, -rownames, -Name, -geneid)
candidates <- candidates %>% drop_na()

head(candidates)

candidates <- as.data.frame(t(candidates))
candidates$RNAseqID <- rownames(candidates)
head(candidates)

candidates <- candidates %>% gather(gene, value, -RNAseqID)  %>% # https://tidyr.tidyverse.org/reference/gather.html
  filter(RNAseqID != "gene")
candidates$value <- as.numeric(candidates$value)
candidates$V1  <- candidates$RNAseqID
head(candidates)

candidatecounts <- left_join(candidates, colData)
#head(candidatecounts)

candidatecounts$faketime <- as.numeric(candidatecounts$treatment)
#head(candidatecounts)

candidatecounts$gene <- as.factor(candidatecounts$gene)
levels(candidatecounts$gene)

p1 <- candidatecounts %>%
  filter(gene %in% c( "AR", "CYP19A1", "ESR1", "ESR2", "FSHR")) %>%
  ggplot(aes(x = treatment, y = value, fill = treatment)) +
  geom_boxplot() +
  facet_wrap(~gene, scales = "free", nrow = 1) +
  theme(axis.text.x = element_blank(),
        legend.position = "bottom") +
  labs(subtitle = "eachgroup")
p1

@@

p2 <- candidatecounts %>%
  filter(gene %in% c("GHRL", "GAL", "NPVF", "GNRH1", "LHCGR")) %>%
  ggplot(aes(x = treatment, y = value, fill = treatment)) +
  geom_boxplot() +
  facet_wrap(~gene, scales = "free", nrow = 1) +
  theme(axis.text.x = element_blank(),
        legend.position = "bottom") +
  labs(subtitle = "eachgroup")
p2

@@

p3 <- candidatecounts %>%
  filter(gene %in% c("PGR", "PRL", "PRLR", "VIP", "VIPR1")) %>%
  ggplot(aes(x = treatment, y = value, fill = treatment)) +
  geom_boxplot() +
  facet_wrap(~gene, scales = "free", nrow = 1) +
  theme(axis.text.x = element_blank(),
        legend.position = "bottom") +
  labs(subtitle = "eachgroup")
p3

>>>>

allcontrasts <- totalDEGS %>%
  ggplot( aes(V1, V2)) +
    geom_tile(aes(fill = V3)) +
    scale_fill_viridis(na.value="#440154", 
                     limits = c(0, 3000),
                     breaks = c(0, 1000, 2000, 3000)) + 
    xlab(" ") + ylab("Timepoint") +
    labs(fill = "# of DEGs",
         subtitle = eachgroup)
plot(allcontrasts)

@@

pca1 <- ggplot(pcadata, aes(treatment, PC1,color = treatment)) + 
  geom_boxplot() +
  ylab(paste0("PC1: ", percentVar[1],"% variance")) +
  xlab(NULL) +
  theme_cowplot(font_size = 8, line_size = 0.25) +
  labs(subtitle = eachgroup) +
  theme(legend.position = "none")

pca2 <- ggplot(pcadata, aes(treatment, PC2,color = treatment)) + 
  geom_boxplot() +
  ylab(paste0("PC2: ", percentVar[2],"% variance")) +
  xlab(NULL) +
  theme_cowplot(font_size = 8, line_size = 0.25) +
  labs(subtitle = eachgroup) +
  theme(legend.position = "none")

@@

sigDEGs <- as.matrix(sigDEGs) 
pheatmap(sigDEGs, show_rownames = F, show_colnames = F,
         color = viridis(30),
         breaks=myBreaks,
         annotation_col=anndf,
         main = eachgroup)

pheatmap(sigDEGs, kmeans_k = 5,
         show_rownames = F, show_colnames = F,
         color = viridis(30),
         breaks=myBreaks,
         annotation_col=anndf,
         main = eachgroup)

@@

# make dataframe with geneids and names and counts
# how to gather: https://tidyr.tidyverse.org/reference/gather.html

candidates <- full_join(geneinfo, DEGs)
drop.cols <-colnames(candidates[,grep("padj|pval|pmin", colnames(candidates))])
candidates <- candidates %>% dplyr::select(-one_of(drop.cols))
candidates <- candidates %>%
  filter(Name %in% c( #"JUN", "JUND", "EGR",  "AVP", "AVPR1A", "AVPR1B", "AVPR2", "OXT",  
                     "AR", "CYP19A1", "ESR1", "ESR2", "FSHR",
                     "GHRL", "GAL", "NPVF", "GNRH1", "LHCGR",
                     "PGR", "PRL", "PRLR", "VIP", "VIPR1")) 
row.names(candidates) <- candidates$Name
candidates <- candidates %>% select(-row.names, -rownames, -Name, -geneid)
candidates <- candidates %>% drop_na()
candidates <- as.data.frame(t(candidates))
candidates$RNAseqID <- rownames(candidates)
candidates <- candidates %>% gather(gene, value, -RNAseqID)  %>% 
  filter(RNAseqID != "gene")
candidates$value <- as.numeric(candidates$value)
candidates$V1  <- candidates$RNAseqID
candidatecounts <- left_join(candidates, colData)
candidatecounts$faketime <- as.numeric(candidatecounts$treatment)
candidatecounts$gene <- as.factor(candidatecounts$gene)

p1 <- candidatecounts %>%
  filter(gene %in% c( "AR", "CYP19A1", "ESR1", "ESR2", "FSHR")) %>%
  ggplot(aes(x = treatment, y = value, fill = treatment)) +
  geom_boxplot() +
  facet_wrap(~gene, scales = "free", nrow = 1) +
  theme(axis.text.x = element_blank(),
        legend.position = "bottom") +
  labs(subtitle = eachgroup)
p1

@@

p2 <- candidatecounts %>%
  filter(gene %in% c("GHRL", "GAL", "NPVF", "GNRH1", "LHCGR")) %>%
  ggplot(aes(x = treatment, y = value, fill = treatment)) +
  geom_boxplot() +
  facet_wrap(~gene, scales = "free", nrow = 1) +
  theme(axis.text.x = element_blank(),
        legend.position = "bottom") +
  labs(subtitle = eachgroup)
p2

@@

p3 <- candidatecounts %>%
  filter(gene %in% c("PGR", "PRL", "PRLR", "VIP", "VIPR1")) %>%
  ggplot(aes(x = treatment, y = value, fill = treatment)) +
  geom_boxplot() +
  facet_wrap(~gene, scales = "free", nrow = 1) +
  theme(axis.text.x = element_blank(),
        legend.position = "bottom") +
  labs(subtitle = eachgroup)
p3
